### 2014-03-10 docs/paper.tex
Note of some stuff to write about.
meek-server 0.2 suports HTTPS. But using HTTPS increases latency a lot.
https://people.torproject.org/~dcf/graphs/meek-server-0.2-https-latency.png
Outline some different usage scenarios.

@@

We were not able to make the system work with Amazon CloudFront nor Akamai.

>>>>

\section{Usage scenarios}

The default usage scenario has a single paid App Engine instance, publicly known and usable by anyone,
with software configured to use the public instance by default.
This way has the greatest usability because there is nothing to upload and nothing to configure.
The number of parties able to analyze users' traffic patterns is somewhat increased:
the path from user to bridge now includes Google and the app operators, not only the ISP and intermediate routers that were there before.
On the other hand, the bridge no longer gets to see users' IP addresses.
In effect, Google and the app become what Tor calls a ``guard node.''
Because Tor is encrypted and integrity-protected, neither Google nor the app operators
are able to read or alter users' communications, but being able to measure packet timings,
for example, is necessary for certain linking attacks.

Users are also free to upload their own personal copy of the App Engine code, as is done with GoAgent.
App Engine imposes bandwidth quotas on unpaid apps, but they are high enough to allow daily web browsing.
In this scenario, Google still has a privileged network position,
but the user's traffic is no longer visible to the operators of the public app instance.
% Outgoing HTTP requests include app id? As good as an IP address.

The code that runs on App Engine is very simple.
It just statelessly copies HTTP requests and responses.
Another usage scenario has the App Engine code ported to another language such as PHP,
so that it can be run in ordinary web hosting environments.
What you lose with a PHP app is Google's unblockability;
the censor may find and individually block the domains
This scenario is still interesting because there are so many places
where such an app can be run, with low cost and minimal setup.
Installing a PHP file on a web host environment is easier than setting up a Tor bridge or SOCKS proxy.
The URLs of PHP bridges could be distributed in a way like BridgeDB.

@@

We were not able to make the system work with Amazon CloudFront nor Akamai.
% Dreamhost? Other HTTPS webhosts with PHP bridge?

%%%%%%%

% HTTPS or not on the App Engine--bridge link.
% HTTPS obscures session ids, equivalent to obscuring TCP connections in other transports.
% Increases latency a lot: \approx 100 ms increased to \approx 350 ms when I tried it in March 2014.
